Depression and suicidality as costly signals of need

### 2021-04-12 Paper.rmd
Removed line of text and confirmed mediation analyses of MA

Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as belief in need of financial support in the pilot study when comparing both *Depression* and *Suicide attempt* (confirm suicide) to *Verbal request*. However, another possibility is that participants viewed the signal as providing information about adversity outside of the signaler's claims. For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with the stronger signals still conveying the severity of the competition between her and her cousin.

 However, the greater impact on likelihood of help than belief found in this study may have also arisen if participants viewed the signal as providing information about adversity outside of the signaler's claims.
## Relevance to costly signaling

>>>>

Support for this interpretation comes from our mediation analyses, which showed that the likelihood of help was largely, but not entirely, mediated by signal's effect on belief in need in this study but totally mediated by belief in need when measured as need of financial support in the pilot study when comparing both *Depression* and *Suicide attempt* to *Verbal request*. However, another possibility is that participants viewed the signal as providing information about adversity outside of the signaler's claims. For example, participants who saw the "brother-in-law" vignette may have thought the daughter was lying about the assault due to jealously over her cousin, with the stronger signals still conveying the severity of the competition between her and her cousin.
